---
output:
  html_document: default
  pdf_document: default
---
```{r}
# load the csv
data <- read.csv("output_result.csv")
```

```{r}
# print data column names
names(data)
```
    
```{r}
data$algo <- factor(data$algo)
data$type <- factor(data$type)
data$format <- factor(data$format)
```

```{r}
library(nortest)
check_lm_normality <- function(lm_model){
  par(mfrow=c(1,2))
  qqnorm(residuals(lm_model));qqline(residuals(lm_model)); 
  plot(fitted(lm_model), residuals(lm_model))
  # ks_test_result <- ks.test(residuals(lm_model), "pnorm")
  # return(ks_test_result)
  ad_test_result <- ad.test(residuals(lm_model))
  return(ad_test_result)
}
```

```{r}
check_data_normality <- function(data){
  par(mfrow=c(1,2))
  qqnorm(data);qqline(data); 
  plot(data)
  ad_test_result <- ad.test(data)
  return(ad_test_result)
}
```
### Interaction
```{r}
interaction_lm <- lm(compression_time ~ algo*(type+format+size+entropy), data=data)
drop1(interaction_lm, test="F")
```


### algo

```{r}
lzw_data <- subset(data, algo == "lzw")
huffman_data <- subset(data, algo == "huffman")


check_data_normality(lzw_data$compression_time)
check_data_normality(huffman_data$compression_time)
```

```{r}
wilcox.test(lzw_data$compression_time, huffman_data$compression_time)
```
We use Wilcos test, it shows the compression ratio of LZW is significantly different than Huffman coding.


### type

```{r}
type_lm <- lm(compression_time ~ type+algo:type, data=data)
check_lm_normality(type_lm)
```

```{r}
library(ARTool)
type_artm <- art(compression_time ~ type*algo, data=data)
anova(type_artm)
```

```{r}
art.con(type_artm, "type")
```

### format

```{r}
format_lm <- lm(compression_time ~ format+format:algo, data=data)
check_lm_normality(format_lm)
```
same
```{r}
format_artm <- art(compression_time ~ format*algo, data=data)
anova(format_artm)
```
same
```{r}
art.con(format_artm, "format")
```

### size
```{r}
size_lm <- lm(compression_time ~ size+size:algo, data=data)
check_lm_normality(size_lm)
```
  
```{r}  
cor.test(data$compression_time, data$size, method="kendall")
```

### entropy
```{r}
entropy_lm <- lm(compression_time ~ entropy+entropy:algo, data=data)
check_lm_normality(entropy_lm)
```
  
```{r}  
cor.test(data$compression_time, data$entropy, method="kendall")
```

### Interaction
```{r}
all_lm <- lm(compression_time ~ algo*(format + size + entropy)-(format + size + entropy), data=data)
drop1(all_lm, test="F")
check_data_normality(all_lm$residuals)
```

```{r}
all_glm <- glm(compression_time ~ algo*(format + size + entropy)-(format + size + entropy), data=data, family=quasipoisson(link="log"))
summary(all_glm)
```


```{r}
exp(coef(all_glm))
```
The reference intercept gives the expected value of compression time for a file compressed with algorithm in Huffman coding, 
type in video, format in flv, size equals to 0 and entropy equals to 0, which is 9.741808e-04. 
Change the format to mp4, the compression  will increase by 1.061703 times.
Change the type from video to image, the format to jpg, the compression  will increase by 1.309448 times. Change the format to png, the compression  will increase by 1.338752 times.
Change the type from video to text, the format to pdf, the compression  will increas by 1.150028 times. Change the format to txt, the compression  will increase by 2.363867e+01 times.
Increase the size by 1 B, the compression  will increase by 1.000028 times; increase the entropy by 1 bit, the compression  will increase by 2.700506 times.

Switch to the LZW algorithm, the compression  will increase by a factor of 5.976163.
Change the format to mp4, the compression  will increase by a factor of 1.061703.
Change the type from video to image, the format to jpg, the compression  will increase by a factor of 1.225860 Change the format to png, the compression  will increase by a factor of 1.279135.
Change the type from video to text, the format to pdf, the compression  will increase by a factor of 1.150028. Change the format to txt, the compression  will increase by a factor of 1.640929.
Increase the size by 1 B, the compression  will increase by 1.000027; increase the entropy by 1 bit, the compression  will increase by a factor of 2.604329.
